Stack Safety is a Security Property

### 2021-04-10 tex/main.tex
One morec

\bcp{If we end up adopting my recent proposal for defining subtraces and
  separating WBCF, I think we can be a bit stronger here: We define stack
  safety in IFC terminology based on the same intuitions as their LSE, but
  we consider (and define) WBCF to be a separate thing---desirable, but
  distinct from safety.  (If we make this argument, we'll need to show an
  example of a program that is stack safe but doesn't have WBCF.)}In this
work, we take the (informal) definitions of WBCF and LSE as a starting
point, but choose a different approach to formalizing them, based on the
technical framework of language-based security~\citep{??}.  We define
trace-based properties of \emph{stepwise stack integrity} and \emph{stack confidentiality}.
In applying these security concepts, we treat each caller-callee pair as mutually distrustful
and view the caller as needing protection from the callee. \apt{Need more explanation of
  ``nesting'' and our novelty factor here? Also about domains??}
{\em Integrity} says that a caller's local data is protected from modification by its callee.
This is vital for local reasoning about the behavior of the caller.
{\em Confidentiality} states that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack.
Together, these properties (informally) capture LSE, as well as the ``temporal stack safety''
notion that data outside of live frames should be inaccessible (which LSE does not address).
We also give a simple trace-based formalization of WBCF, which is essential for keeping the
notions of ``caller' and ``callee'' sensible.

>>>>

\bcp{If we end up adopting my recent proposal for defining subtraces and
  separating WBCF, I think we can be a bit stronger here: We define stack
  safety in IFC terminology based on the same intuitions as their LSE, but
  we consider (and define) WBCF to be a separate thing---desirable, but
  distinct from safety.  (If we make this argument, we'll need to show an
  example of a program that is stack safe but doesn't have WBCF.)}In this
work, we take the (informal) definitions of WBCF and LSE as a starting
point, but choose a different approach to formalizing them, based on the
technical framework of language-based security~\citep{??}.  We define
trace-based properties of \emph{stepwise stack integrity} and \emph{stack confidentiality}.
In applying these security concepts, we treat each caller-callee pair as
mutually distrustful, with the caller needing protection from the callee. \apt{Need more explanation of
  ``nesting'' and our novelty factor here? Also about domains??}
{\em Integrity} says that a caller's local data is protected from
modification by its callee.\bcp{What about the ``stepwise'' part?}
This is vital for local reasoning about the behavior of the caller.
{\em Confidentiality} states that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack.
Together, these properties (informally) capture LSE, as well as the ``temporal stack safety''
notion that data outside of live frames should be inaccessible (which LSE does not address).
We also give a simple trace-based formalization of WBCF, which is essential for keeping the
notions of ``caller' and ``callee'' sensible.
